---
title: "group assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Group 5
Alice, Faten, Zineb, Debora
Regression data R1
http://users.stat.ufl.edu/~winner/data/airline_costs.txt
http://users.stat.ufl.edu/~winner/data/airline_costs.dat

J.W. Proctor and J.S. Duncan (1954). "A Regression Analysis
of Airline Costs," Journal of Air Law and Commerce, Vol.21, #3
https://scholar.smu.edu/cgi/viewcontent.cgi?article=2903&context=jalc


                infos:

submit as pdf by email noon 16.4. first draft, noon 20.6. final

include relevant plots (must look nice)
No raw R code
see lab2
12 pt font, 2,5 cm margins, our surnames in top margin, number pages at bottom, 3-5 pages max, no cover page
 


                outline: 

give background, state the problem of interest (aim of original study)

exploratory data analysis EDA

model fitting and selection analysis

model assessment, justify the results

final model (written in mathematical terms), include evtl shortcomings of this model 

conclusion, address problem of interest

```{r plot}

data = read.csv("airline_costs.dat", head=FALSE, sep="")

par(mfrow = c(2,4))

plot(log(data$V6) ~ log(data$V2))
plot(log(data$V6) ~ log(data$V3))
plot(log(data$V6) ~ log(data$V4))
plot(log(data$V6) ~ log(data$V5))
plot(log(data$V6) ~ log(data$V7))
plot(log(data$V6) ~     data$V8)
plot(log(data$V6) ~ log(data$V9))
plot(log(data$V6) ~ log(data$V10))

```


```{r boxplots}

par(mfrow = c(2,5))

boxplot(data$V2, main = "V2")
boxplot(data$V3, main = "V3")
boxplot(data$V4, main = "V4")
boxplot(data$V5, main = "V5")
boxplot(data$V6, main = "V6")
boxplot(data$V7, main = "V7")
boxplot(data$V8, main = "V8")
boxplot(data$V9, main = "V9")
boxplot(data$V10, main = "V10")
boxplot(data$V12, main = "V12")

par(mfrow = c(1,1))

```

```{r log model}

mod <- lm(log(data$V6) ~ log(data$V2)+log(data$V3)+log(data$V4)+log(data$V5)+data$V8+log(data$V9)+log(data$V10)-1)

# do we want V10 (total assets) or V12 (adjusted assets)?
# source: important: V8, V9, V4
#        not important: V2, V5, V3, V10

# V1 Airline
# V2 Length of flight (miles)         
# V3 Speed of Plane (miles per hour)  
# V4 Daily Flight Time per plane (hours)
# V5 Population served (1000s)        
# V6 Total Operating Cost (cents per revenue ton-mile)
# V7 Revenue Tons per Aircraft mile
# V8 Ton-Mile load factor (proportion)  
# V9 Available Capacity (Tons per mile)  
# V10 Total Assets  ($100,000s)         
# V11 Investments and Special Funds  ($100,000s)
# V12 Adjusted Assets  ($100,000s)

summary(mod)
```


```{r smaller models}
mod2 <- lm(log(data$V6) ~ log(data$V3)+data$V8+log(data$V9)-1)
#conclusion from model above
summary(mod2)
plot(mod2)

mod3 <- lm(log(data$V6) ~ log(data$V4)+data$V8+log(data$V9)-1)
#suggested in source
summary(mod3)
plot(mod3)
```


```{r without influential obervation}
data2 <- data
data2[6,] <- NA
data2[30,] <- NA

modbis <- lm(log(data2$V6) ~ log(data2$V2)+log(data2$V3)+log(data2$V4)+log(data2$V5)+data2$V8+log(data2$V9)+log(data2$V10)-1)
summary(modbis)
par(mfrow = c(2,2))
plot(modbis)

mod2bis <- lm(log(data2$V6) ~ log(data2$V3)+data2$V8+log(data2$V9)-1)
summary(mod2bis)
plot(mod2bis)
```






